\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-21 ms/adult.tex
Add map porn
Add map of party identification and porn consumtpion by US states.

Overall, we have over 6 million web browsing records by the 1,200 individuals over the one-month period of June 2022. 
For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. Individuals are spread out over the US states and regions (see \cref{fig:map_duration}). 
Our data also comes with characteristics for the 1,200 individuals.
We have information on their party identification, which we use to code their partisanship.
We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
Out of the 1,080 individuals who report party identification, the majority 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
In the analyses focusing on splits by party, we use only those who lean either Republican or Democrat.
We also have information on birth year, gender, race, and education level.
\cref{tab:characteristics_split_by_party} shows differences in gender, and race(?) by party. 
Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.

@@

>>>>

Overall, we have over 6 million web browsing records by the 1,200 individuals over the one-month period of June 2022. 
For each web browsing activity, we have information on the domain (e.g., wikipedia.org), the time of visit, and the time spent on the domain. Individuals are spread out over the US states and regions (see \cref{fig:map_porn}). 
Our data also comes with characteristics for the 1,200 individuals.
We have information on their party identification, which we use to code their partisanship.
We verify this using information on whether they voted for the Republican or Democratic candidate in the 2020 presidential election.
Most individuals reported their party identification, with 120 individuals who did not respond or say not sure/don't know.
Out of the 1,080 individuals who report party identification, the majority 82 percent lean either Republican or Democrat. The remaining 18 percent identify as independent.
In the analyses focusing on splits by party, we use only those who lean either Republican or Democrat.
We also have information on birth year, gender, race, and education level.
\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.
Republicans in the sample are, on average, older, less likely to be female, and much more likely to be White.
Hence, our analyses below for differences in porn consumption includes these characteristics in the estimation.

@@

%============================================================================
% Map of party identification
%============================================================================
\begin{figure}
	\centering
	\caption{Party Identification by States}
	\begin{subfigure}[t]{0.7\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../figs/map_pid7.pdf}
		\caption{Partisanship}
	\end{subfigure}
	\caption*{\footnotesize \emph{Notes:} 
		Redder colors indicate stronger identification to the Republican party.
		Bluer colors indicate stronger identification to the Democratic party.
		North Dakota and Vermont have no data (shaded out).
	}
	\label{fig:map_pid7}
\end{figure}

\begin{figure}[t]
	\caption{Porn Consumption by State}
	\label{fig:map_porn}
	\centering
	\begin{subfigure}[t]{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../figs/map_visits.pdf}
		\caption{Percentage of visits to porn sites}
	\end{subfigure}
	\begin{subfigure}[t]{0.8\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../figs/map_duration.pdf}
		\caption{Percentage of duration on porn sites}
	\end{subfigure}
	\caption*{\footnotesize \emph{Notes:} 
		Darker shades indicate higher values.
		Values for each state are percentage of visits to and time spent on porn sites averaged across individuals of the states.
		Baseline values are for all web browsing activity.
		North Dakota and Vermont have no data (shaded out).}
\end{figure}
